The host galaxy of the short GRB~111117A at $z = 2.211$\thanks{Based on observations collected at the European Southern Observatory, Paranal, Chile, Program ID: 088.A-0051 and 091.D-0904.}

### 2017-06-01 GRB111117A.tex
Christinas comments
Contained partly in Nials comments. Closes #5

In this \emph{Letter}, we have provided a revised, spectroscopic redshift for the short
GRB~111117A based on emission lines %discovered using an improved reduction scheme, 
setting it at $z = 2.211$. This value supersedes and corrects the previous
photometric redshift of \citet{Margutti2012} and \citet{Sakamoto2013}. The erroneous redshift estimate of previous authors is attributed to a discrepancy in the measured $z$-band magnitude.

The rest-frame parameters of the burst and the conditions of the burst
environment have been recalculated using the new distance. The X-ray derived
hydrogen column density towards GRB~111117A is the highest within a complete
sample of short hosts, but is indicative of an evolution with redshift as found
for the hosts of long GRBs.

>>>>

In this \emph{Letter}, we have provided a revised, spectroscopic redshift for
the short GRB~111117A based on emission lines setting it at $z = 2.211$. This
value supersedes the previous photometric redshift of \citet{Margutti2012} and
\citet{Sakamoto2013}. %The erroneous redshift estimate of previous authors is
attributed to a discrepancy in the measured $z$-band magnitude.

The rest-frame parameters of the burst and the conditions of the burst
environment have been recalculated using the new distance. The X-ray derived
hydrogen column density towards GRB~111117A is the highest within a complete
sample of short hosts and is indicative of an evolution with redshift as found
for the hosts of long GRBs.
